\graphicspath{{./figures/}}
\chapter{Tasks}
This chapter provides an overview over all tasks that are approached in this
project.
Hardware related tasks are listed as well as software related tasks.
Each main task is divided into several sub-tasks.

\begin{description}
    \item[Task 1] Develop a platform independent computer software to analyze 
    pre-recorded long-jump videos.
    \begin{enumerate}
        \item Integrate a body detection system.
        \item Define an analysis output standard.
        \item Develop an algorithm to automatically detect the take-off frame. 
        \item Implement a \acs*{GUI} to visualize analysis results.
    \end{enumerate}
    \item[Task 2] Build a quadcopter as hardware companion for recording 
    long-jump videos. This specifically requires a camera as well as several
    sensors for navigation.
    \begin{enumerate}
        \item Select hardware components according defined criteria.
        \item Build a flying quadcopter that is controllable from a ground
        station.
        \item extend the quadcopter with a companion computer and a compatible
        camera to live stream videos.
        \item test the camera accuracy.
    \end{enumerate}
    \item[Task 3] Implement a software that allows to control the drone from a
    ground station.
    \begin{enumerate}
        \item Set up a wireless connection to the quadcopter.
        \item Define a communication protocol.
        \item Integrate the control mechanism in the \acs*{GUI}.
        \item Integrate a start measurement like mechanism.
    \end{enumerate}
    \item[Task 4] Develop a software to handle the incoming video livestream.
    \begin{enumerate}
        \item Establish a connection to the on-board companion computer.
        \item Display the video frames in the \acs*{GUI}.
        \item Offer the option for a rudimentary live analysis.
    \end{enumerate}
    \item[Task 5] Develop a software that can control the drone autonomously.
    \begin{enumerate}
        \item Establish between an on-board companion computer and PixHawk
        flight controller.
        \item Implement an on-board body detection system.
        \item Develop an auto-follow like controlling feature. 
    \end{enumerate}
\end{description}
