\graphicspath{{./figures/}}
\chapter{Results}\label{chapt:5_res}
This chapter provides an overview of the tasks defined in \autoref{chapt:2_tasks}
and their respective completion states.\\
With the exception of three (sub-) tasks, all tasks were fulfilled.
All of them are described in detail in \autoref{chapt:4_implementation}.
All in all it can be said that the developed long-jump analysis tool is able
to record and analyze long-jump videos.
However, following limitations need to be considered:
\begin{itemize}
    \item The jump recording must be of high quality and well-resolved in the time domain.
    \item The flying conditions must be sufficient (e.g. not too much wind or other disturbances).
    \item The live-stream connection only works in small distance to the drone. 
\end{itemize}

\noindent \autoref{table:5_completed_tasks} gives an overview of completed and
uncoompleted tasks.
Tasks that are not fully implemented are parenthesised.
Tasks that are not implemented at all are marked with a crossmark. 

\begin{longtable}{ |c|p{12cm}|c| }
    \caption{Your caption here} \label{table:5_completed_tasks} \\
    \hline
    \rowcolor{gray!20}
    \multicolumn{3}{|c|}{Task completion states}\\
    \hline
    Task No. & Task description & Status\\
    \hline
    \hline
    \endfirsthead
    \multicolumn{3}{c}%
    {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
    \hline
    Task No. & Task description & Status\\
    \hline
    \endhead
    \hline \multicolumn{3}{|r|}{{Continued on next page}} \\ \hline
    \endfoot
    \hline
    \endlastfoot
    \multirow{2}{*}{1} & \cellcolor{cyan!15}Develop a platform independent computer software to analyze pre-recorded long-jump videos. & \multirow{2}{*}{$\checkmark$}\\
    \hline
    1.1 & Implement a video processing pipeline to analyse a jump regarding a fixed set of parameters. & $\checkmark$\\
    \hline
    1.2 & Develop an algorithm to automatically detect the take-off frame. & $\checkmark$\\
    \hline
    1.3 & Define and implement an analysis output standard. & $\checkmark$\\
    \hline
    1.4 & Validate the performance to allow on-field jump analysis. & $\checkmark$\\
    \hline
    1.5 & Implement a \acs*{GUI} to visualize the analysis results. & $\checkmark$\\
    \hline
    \multirow{2}{*}{2} & \cellcolor{cyan!15}Build a quadcopter as hardware companion for recording long-jump videos. This specifically requires a camera as well as several sensors for navigation. & \multirow{2}{*}{$\checkmark$}\\
    \hline
    2.1 & Select hardware components according defined criteria. & $\checkmark$\\
    \hline
    2.2 & Build a flying quadcopter that is controllable from a ground station. & $\checkmark$\\
    \hline
    2.3 & Extend the quadcopter with a companion computer and a compatible camera to live stream and record videos which can be analyzed. & $(\checkmark)$\\
    \hline
    \multirow{2}{*}{3} & \cellcolor{cyan!15}Implement a software that allows to manually and automatically control the drone & \multirow{2}{*}{$(\checkmark)$}\\
    \hline
    3.1 & Set up a wireless connection to the quadcopter. & $\checkmark$\\
    \hline
    3.2 & Implement a drone control offering movement control. & $\checkmark$\\
    \hline
    3.3 & Implement a drone control offering movement control. & $\checkmark$\\
    \hline
    3.4 & Implement an auto-follow like feature. & \newcrossmark \\
    \hline
    4 & \cellcolor{cyan!15}Develop a software to handle the incoming video livestream. & $(\checkmark)$\\
    \hline
    4.1 & Establish a connection to the on-board companion computer. & $\checkmark$\\
    \hline
    4.2 & Display the video frames in the \acs*{GUI}. & $\checkmark$\\
    \hline
    4.3 & Offer the option for a rudimentary live analysis. & \newcrossmark \\
    \hline
\end{longtable}
\FloatBarrier
Not finished tasks are in particular:
\begin{itemize}
    \item Task 2.3: Both parts of the project, namely the video based long-jump
    analysis tool and the drone itself have been successfully tested.
    However, due to poor testing conditions, the video software is yet to be
    tested with actual drone footage.
    \item Task 3.4: Approaches towards a camera based auto follow feature
    have been made using OpenCV.
    However, the live evaluation of video frames to keep the athlete centered
    in the frame have been found not to be reliable enough to let the on-board
    RaspberryPi control the drone's flight path to ensure a safe video
    capturing process.
    \item Task 4.3: A long-jump live analysis heavily relies on the received
    drone's live-stream.
    As aforementioned however, the live-stream quality in this project is limited
    not to consume too much bandwidth.
\end{itemize}
